A weighted sampling algorithm to designing RNA sequences with target secondary structure and nucleotide distribution

### 2013-01-08 ISMB/results_ISMB.tex
add section of comparison with local

\subsection{Global sampling, Local search and Glocal approach}

>>>>

\subsection{Global sampling vs Local search vs Glocal approach}
Here, we are interested in estimating the impact of the design methodology on the performances. More precisely, we aim to what are the benefits of a global sampling approach (\ourprog), versus a glocal procedure (\ourprog + \RNAinverse) or the classical local search methodology (\RNAinverse). Thus, we compare our method to a pure local search procedure. In particular, here we compare to \RNAinverse as it is the program we used to do the local optimization (see Section \ref{subsec:glocal_method}). Our results (See Fig. \ref{fig:rnainverse} in Supplementary data) show that \ourprog overcome other strategies. In particular, the base pair entropy as well as diversity of sequences are favorable to \ourprog. This advantage is even more striking for low \gc~content regimes.

To complete this benchmark, we added the results obtained with the glocal procedure (\ourprog + \RNAinverse). We note that the results are slightly lower than those of \ourprog alone. However, we must stress that the \ourprog data consider only the sample of \ourprog already satisfying the MFE criterion. In fact \RNAinverse enable to ``correct'' a lot of sample sampled by \ourprog but without the good folding properties. Hence, our conclusion here is that the glocal approach \ourprog + \RNAinverse enable us to conserve the same level of performance but to drastically improve the success rate of our methodology.
